Endogenous Politics and \\ the Design of Trade Institutions

### 2016-07-20 feedback.tex
add feedback from 2016 PEIO presentation

>>>>

\newpage
\subsection{January 2016, PEIO Salt Lake City}
\begin{itemize}
	\item Elias Bengtsson: more on policy implications, who's doing what to whom
	\item Cristiane Carneiro
		\begin{itemize}
			\item Flexible instruments
			\item Agreement duration, exit (legal scholarship)
			\item Look at Summer 2001 special edition of IO
			\item Korgmenos 2013 JCR
			\item Korgmenos and Nav 2011
			\item Coil
			\item Helper 2005, Virginia Law Review
		\end{itemize}
	\item Renee Bowen: what's the contribution relative to GH; her paper, Peter's, McLaren (but she was a bit confused about what I was doing we figured out later)
	\item Competing lobbies--exporters
	\item Peter: $\ga(e)$ and $\ga(s)$ combination is interesting, so it dyanmic choice of protection over time, gov't turnover
\end{itemize}
